---
title: "Cost Analysis"
date: "02/06/2015"
output:
    html_document:
        toc: true
        toc_depth: 4
        number_sections: true
---




#Cost Analysis


```{r,echo=F,results='hide', warning=F,message = F}

opts_chunk$set(comment=NA, fig.height=5, fig.width=7, fig.align='center')
knitr::opts_chunk$set(cache=TRUE)
knitr::opts_chunk$set(dev='png')

source("LoadData.R")
source("./SmallScripts/Utility.r")
library("ggplot2")
library("xtable")
library("GGally")
library("scales")
library("reshape")
library("plyr")
PublicFac  <- c("PH","DH","HC")

```

## OutPatient

### Check Number of Out Patient Records
```{r,echo=F,results='html'}

cat("Total number of OutPatient Cost Reports")
cat(sum(OutPat$Q==1))

cat("Total number of OutPatient Cost Reports")
print(sapply(OutPatGroups,sum))

```

### Outpatient Tables

#### Number of Outpatient cost reports by Facility
```{r , echo=F, results='asis'}

printt(

    sapply (levels(OutPat$Facility),function(F){
  sapply(OutPatGroups,function(G){ length(subset(OutPat[G,],Facility==F)[,1]) })
})

,"Number fo Outpatient cost reports by facility")

```

##### Plot of Outpatient cost reports  by Facility
```{r , echo=F, results='asis', fig.height=5}


OutPatCounts = transform(summarise(group_by(OutPat,Group, Facility),Count=length(Total)))
OutPatCounts <- cbind(OutPatCounts,
                      Events = sapply(1:length(as.data.frame(OutPatCounts)[,1]),function(X){
                        with(OutPatCounts[X,], sum(IH[,paste("Care_At",Facility,sep="_")] & IH$Group == Group))
                      }))


OutPatCounts$Events[OutPatCounts$Facility %in% InOutCare] <- 
  sapply(1:length(as.data.frame(OutPatCounts)[OutPatCounts$Facility %in% InOutCare,"Events"]),function(X){
    with(OutPatCounts[OutPatCounts$Facility %in% InOutCare,][X,],
         sum(IH[,paste("Overnight_At",Facility,sep="_")]=="Day"
             & IH$Group == Group))
  })
    

p <- ggplot(data=OutPat,aes(x=Facility,fill=Group))
p <- p + geom_histogram()
p <- p + labs(title="Outpatient Cost Report Count by Facility")
p <- p + stat_bin(geom="text", aes(label=sprintf(..count..,fmt="%d")),vjust=-.5,size=3)
p <- p + geom_text(data=OutPatCounts,aes(x=Facility,y=Count, label= sprintf(100*Count/Events,fmt="%.1f%%")),size=3,vjust=1)
p <- p + facet_grid(Group~.)
p

```

##### Plot of Outpatient Useage rates by Facility
```{r , echo=F, results='asis',fig.height=5}



IHMelt <- melt(IH[,c("Serial",
                     "Group",
                     names(IH)[grep("Overnight_At",names(IH))])],
               id=c("Serial","Group"))
names(IHMelt)[3]="Facility"

p <- ggplot(data=subset(IHMelt,value=="Day"), aes(x=Facility,fill=Group))
p <- p + geom_bar(aes(x=Facility,fill=Group))
p <- p + scale_x_discrete(labels=sub("Overnight_At_","",levels(IHMelt$Facility)))
p <- p + theme(axis.text.x = element_text(angle = 90, hjust = 1))
p <- p + labs(title="Outpatient Useage rates by Facility")
p <- p + stat_bin(geom="text", aes(label=sprintf(..count..,fmt="%d")),vjust=1,size=3)
p <- p + facet_grid(Group~.)
print(p)

```    

### Plot Outpatient Totals By Facility
```{r ,echo=F, results='asis',warning=F, messag=F}




library(dplyr)
OutPatMeans = transform(summarise(group_by(OutPat,Group, Facility), Total = mean(Total)), 
                    Label = format(Total,digits=0,big.mark=',',scientific=FALSE))


p <- ggplot(data=OutPat,aes(x=Facility,y=Total,color=Group))
p <- p + labs(title="Outpatient Event Cost Means (Full range)")
p <- p + geom_point(position=position_jitter(w=0,h=0),
                    alpha=.35,
                    shape=95,
                    size=10)
p <- p + scale_y_continuous(name="Cost in LAK",labels=comma)
p <- p + facet_grid(Group~.)
p <- p + stat_summary(fun.data = "mean_cl_boot", colour = "black")
p <- p + geom_text(data=OutPatMeans,aes(label = Label), size=3,angle = 90, vjust=2,hjust = -.6, color="black")
print(p)

p <- p + labs(title="Outpatient Event Cost Means (<750000)")
p <- p + coord_cartesian(ylim = c(0, 750000))
print(p)

```

### Plot Outpatient Costs by Cost Type, Service, and Group
```{r ,echo=F, results='asis',warning=F}

OutPCostBreakDown <-  melt(data=OutPat[,c("Medical_Fee","Medicine","Others","Transport","Total","Serial","Facility","Group")],id.vars=c("Serial","Facility","Group"))
OutPCostBreakDown <- subset(OutPCostBreakDown,!is.na(value))

stat_sum_single <- function(fun, geom="point", ...) {
  stat_summary(fun.y=fun, colour="red", geom=geom, size = 1, ...)
}
p <- ggplot(data=OutPCostBreakDown,aes(x=variable,y=value))
p <- p + geom_point()
p <- p + stat_sum_single(mean)
p <- p + facet_grid(Group~Facility)
p <- p + theme(axis.text.x = element_text(angle = 90, hjust = 1))
p <- p + coord_cartesian(ylim = c(0, 750000))
p <- p + scale_y_continuous(name="Cost in LAK",labels=comma)
p <- p + labs(title="Outpatient Cost Breakdown",x="")
print(p)
                    
```

### Outpatient PH Details
```{r ,echo=F, results='asis',warning=F}

stat_sum_single <- function(fun, geom="point", ...) {
  stat_summary(fun.y=fun, colour="red", geom=geom, size = 3, ...)
}
p <- ggplot(data=subset(OutPCostBreakDown,Facility=="PH"),aes(x=variable,y=value))
p <- p + geom_point()
p <- p + stat_summary(fun.data = "mean_cl_boot", colour = "red")
p <- p + facet_grid(.~Group)
p <- p + theme(axis.text.x = element_text(angle = 90, hjust = 1))
p <- p + coord_cartesian(ylim = c(0, 750000))
p <- p + scale_y_continuous(name="Cost in LAK",labels=comma)
p <- p + labs(title="Outpatient Cost Breakdown",x="")
print(p)




OOPLabler <- function(variable,value){
  return(ifelse(value,"OOP","No-OOP"))
}

OutPCostBreakDown

OutPCostBreakDown2 = transform(summarise(group_by(OutPat,Group, Facility), Total = mean(Total)), 
                    Label = format(Total,digits=0,big.mark=',',scientific=FALSE))


OutPCostBreakDown2 <- melt(with(subset(OutPCostBreakDown, variable=="Total"),
                                table(Facility,Group)),
                           id.vars=Facility)



p <- ggplot(data=subset(OutPCostBreakDown,Facility %in% PublicFac & variable=="Total"),
            aes(x=Group,fill=value!=0))
p <- p + geom_bar()
p <- p + stat_bin(geom="text", aes(label=sprintf(..count..,fmt="%d")),vjust=1,size=3)
p <- p + scale_fill_manual("Payment:",values=c("darkgreen","darkred"),labels=c("No-OOP","OOP"))
p <- p + stat_density(geom="text", aes(label=sprintf(..density..*100,fmt="%.1f%%")),vjust=-1,size=3)
p <- p + facet_grid(.~Facility)
print(p)
  

    sum(subset(OutPCostBreakDown,variable=="Total")==0)


```



### Plot Public Health Facility HEF Level Outpatient Costs by Cost Type, Srvice, and Group
```{r ,echo=F, results='asis',warning=F}

p <- ggplot(data=subset(OutPCostBreakDown,Facility %in% PublicFac ),aes(x=variable,y=value))
p <- p + geom_point(shape=95,fill="Black",
##                    position=position_jitter(w=.1,h=0),
                    size=10,
                    alpha=.1)
p <- p + facet_grid(Group~Facility)
p <- p + theme(axis.text.x = element_text(angle = 90, hjust = 1))
p <- p + scale_y_continuous(name="Cost in LAK",labels=comma)
p <- p + scale_x_discrete("Cost Type")
p <- p + stat_summary(fun.data = "mean_cl_boot", colour = "red")
p <- p + labs(title="Costs by Facility, Cotst Type, and Insurance Group")
print(p)

p <- p + coord_cartesian(ylim = c(0, 150000))
print(p)

```






## InPatient

### Check Number of In Patient Records
```{r,results='html' ,warning=F}

##Check the total number of InPatient Events
length(InPat$Q)


##Check the total number of InPatient Events
sapply(InPatGroups,sum)

```

### Plot Inpatient Totals By Facility
```{r ,echo=F, results='asis',warning=F}


p <- ggplot(data=InPat,aes(x=Facility,y=Total))
p <- p + geom_point(shape=95,fill="Black",
                    size=10,
                    alpha=.2)
p <- p + facet_grid(Group~.)
p <- p + stat_summary(fun.data = "mean_cl_boot", colour = "red")
print(p)

p <- p + coord_cartesian(ylim = c(0, 2000000))
print(p)

```

### Plot Inpatient Totals By Facility with group
```{r ,echo=F, results='asis' ,warning=F}

p <- p + facet_grid(Group~.)
print(p)

p <- p + coord_cartesian(ylim = c(0, 50000))
print(p)

```

### Plot Inpatient Costs by Cost Type, Srvice, and Group
```{r ,echo=F, results='asis' ,warning=F}

InPCostBreakDown <-  melt(data=InPat[,c("Medical_Fee","Medicine","Others","Transport","Total","Serial","Facility","Group")],id.vars=c("Serial","Facility","Group"))
InPCostBreakDown <- subset(InPCostBreakDown,!is.na(value))

p <- ggplot(data=InPCostBreakDown)
p <- p + geom_point(aes(x=variable,y=value))
p <- p + facet_grid(Group~Facility)
p <- p + theme(axis.text.x = element_text(angle = 90, hjust = 1))
p <- p + coord_cartesian(ylim = c(0, 750000))
print(p)
                    
```

### Plot Public Health Facility HEF Level Inpatient Costs by Cost Type, Srvice, and Group
```{r ,echo=F, results='asis'}

p <- ggplot(data=subset(InPCostBreakDown,Facility %in% PublicFac ),aes(x=variable,y=value))
p <- p + geom_point(shape=95,fill="Black",
                    ## position=position_jitter(w=.25,h=0),
                    size=10,
                    alpha=.2)
p <- p + stat_summary(fun.data = "mean_cl_boot", colour = "red")
p <- p + facet_grid(Facility~Group)
p <- p + theme(axis.text.x = element_text(angle = 90, hjust = 1))
p <- p + scale_y_continuous(name="Cost in LAK",labels=comma)
p <- p + scale_x_discrete("Cost Type")
p <- p + labs(title="Costs by Facility, Cotst Type, and Insurance Group")
print(p)

p <- p + coord_cartesian(ylim = c(0, 500000))
print(p)

```

## Model
```{r,echo=F,results='asis'}

InPat$ModelID <-factor( paste(InPat$Group,InPat$Facility))
ModelMeans <- sapply(levels(InPat$ModelID),function(M){mean(subset(InPat,ModelID==M)[,"Total"])})
InPat$ModelID <-factor(InPat$ModelID,levels=levels(InPat$ModelID)[order(ModelMeans)])

p <- ggplot(data=InPat,aes(x=ModelID,y=Total))
p <- p + geom_point(shape=95,size=10,alpha=.1,na.rm=T)
p <- p + stat_summary(fun.data = "mean_cl_boot", colour = "red")
p <- p + stat_summary(fun.y = median, colour="blue",geom="point")
p <- p + theme(axis.text.x = element_text(angle = 90, hjust = 1))
print(p)

p <- p + coord_cartesian(ylim = c(0, 5000000))
print(p)

p <- p + coord_cartesian(ylim = c(0, 50000))
print(p)

```

###OOP
```{r}

sapply(InPatGroups,function(G){
  sapply(levels(InPat$Facility),function(F) {
    mean(subset(InPat[G,],Facility==F)[,"Total"])
  })})


InPat$HavePhone <- lps$HH_Posses_Mobile_phone[InPat$Serial] > 0
InPat$OOP <- InPat$Total > median(subset(InPat,Facility=="PH")$Total)
mylogit <- glm(OOP ~ Age + 
                 Group +
                 NumIllnesses +
                 HavePhone + 
                 WPCA.NPeople +
                 WPCA.Sex +
                 WPCA.Lit1 +                                 
                 WPCA.Lit2 +                                 
                 WPCA.NCH  +                                
                 WPCA.NAdult +                                
                 WPCA.House +                              
                 WPCA.Roof +                               
                 WPCA.TV  +                                
                 WPCA.Vid  +                                 
                 WPCA.Bike  +                                
                 WPCA.Moto   +                               
                 WPCA.Tractor +                              
                 WPCA.Toilet  +                             
                 WPCA.Energy  +                             
                 WPCA.Cereals +                             
                 WPCA.Shop    +                             
                 WPCA.NChic   +                             
                 WPCA.NPig    +                             
                 WPCA.NCattel+
                 WPCA.Cash   ,
               data = subset(InPat,Facility=="PH"), family = "binomial")


summary(mylogit)
Pr <-predict(mylogit,type="response")
qplot(Pr)

P <- cbind.data.frame(Pr = Pr[order(Pr)],
                      OOP=as.numeric(subset(InPat,Facility=="PH")$OOP[order(Pr)]),
                      Ord=order(subset(InPat,Facility=="PH")$Total[order(Pr)])/length(subset(InPat,Facility=="PH")$OOP)
                      )
p <- ggplot(data=P,aes(x=1:length(Pr)))
p <- p + geom_point(aes(y=Pr),color="Blue")
p <- p + geom_point(aes(y=OOP),color="Red")
p <- p + geom_point(aes(y=Ord),color="Green")
print(p)

p <- p + coord_cartesian(xlim = c(0, 50))

c("Group","Gender","Age","NumIllnesses","Marital_Status","WPCA.NPeople","WPCA.Sex","WPCA.Lit1","WPCA.Lit2","WPCA.NCH","WPCA.NAdult","WPCA.House","WPCA.Roof","WPCA.TV","WPCA.Vid","WPCA.Bike","WPCA.Moto","WPCA.Tractor","WPCA.Toilet","WPCA.Energy","WPCA.Cereals","WPCA.Cash","WPCA.Shop","WPCA.NChic","WPCA.NPig","WPCA.NCattel")
ggpairs(InPat[predict(mylogit)<.65,c("Group","Age","NumIllnesses")])
      ## "WPCA.NPeople","WPCA.Sex","WPCA.Lit1","WPCA.Lit2","WPCA.NCH","WPCA.NAdult","WPCA.House","WPCA.Roof","WPCA.TV","WPCA.Vid","WPCA.Bike","WPCA.Moto","WPCA.Tractor","WPCA.Toilet","WPCA.Energy","WPCA.Cereals","WPCA.Cash","WPCA.Shop","WPCA.NChic","WPCA.NPig","WPCA.NCattel")])



plot(exp(predict(mylogit,InPat[order(InPat$Total),])))
plot(InPat[order(InPat$Total),"Total"]==0,color="Blue",dad=T)

```




#catastrophic
```{r,echo=F,results='asis'}

all <- c("1_Total_cost_Overall_average","2_Total_cost_Overall_average","3_Total_cost_Overall_average")

V1 <- !is.na(AllResp[,"1_Indiv"])
V2 <- !is.na(AllResp[,"2_Indiv"])
V3 <- !is.na(AllResp[,"3_Indiv"])


NOutP      <- sapply(levels(lps$Group), function(G){length(subset(OutPat,G==Group)[,1])})
OutP_G500K <- sapply(levels(lps$Group), function(G){sum(subset(OutPat,G==Group)$Total>500000,na.rm=T)})
OutP_G1M   <- sapply(levels(lps$Group), function(G){sum(subset(OutPat,G==Group)$Total>1000000,na.rm=T)})
OutP_20Per <- sapply(levels(lps$Group),
                     function(G){
  sum(subset(OutPat,G==Group)$Total
      > .2*lps[subset(OutPat,G==Group)$Serial,]$HH_Cash_income)})
NInP       <- sapply(levels(lps$Group), function(G){length(subset(InPat,G==Group)[,1])})
InP_G500K  <- sapply(levels(lps$Group), function(G){sum(subset(InPat,G==Group)$Total>500000,na.rm=T)})
InP_G1M    <- sapply(levels(lps$Group), function(G){sum(subset(InPat,G==Group)$Total>1000000,na.rm=T)})
InP_20Per <- sapply(levels(lps$Group),
                     function(G){
  sum(subset(InPat,G==Group)$Total
      > .2*lps[subset(InPat,G==Group)$Serial,]$HH_Cash_income)})



CatTab <- rbind(NOutP     ,
                OutP_G500K,
                OutP_G1M  ,
                OutP_20Per,
                NInP      ,
                InP_G500K ,
                InP_G1M,
                InP_20Per)

print(xtable(CatTab,"Catastrophic Expenditure for single events"),type='html')


```




```{r}


ScoreMeans <- ddply(lps[,c("Village","Score")],.(Village),summarize,
                    Sd= sd(Score),Score = mean(Score)
                    )

p <- ggplot(data=lps)
p <- p + geom_point(aes(color=Group,x=factor(Village,levels=ScoreMeans$Village[order(ScoreMeans$Score)]),y=Score))
print(p)

```
