---
title: "Cost Modeling Investigation"
date: "02/06/2015"
output: html_document
---
# Background
This is an R Markdown exploratory analysis of Cost Modeling

A model is created based on the mean and median values of each service type for each demographic.
The mean is melded with the median to decrease the outlier effects while still allowing them to drive some of the input.

The model is implemented for each individual, each service used is assigned it's model cost for that individual. Any known costs are used instead of the model when available.
In this way we get the influence of the individual usage rates.


```{r,echo=F,results='hide'}

library("ggplot2")
library("xtable")
load("InitialAnalysis.RData")
source("./SmallScripts/Utility.r")
source("LoadData.R")

```

# Summary of Estemation Results

### Mean Total Costs by Indv
```{r,echo=F,results='asis'}

CostByIndv <- rbind(Mean=sapply(ligroups,function(G){mean(IndiHealth$CostTot[G])}),
                       Median=sapply(ligroups,function(G){median(IndiHealth$CostTot[G])}))
CostByIndvF <- formatC(CostByIndv,digits=0,format="f",big.mark=",")
print(xtable(CostByIndvF),type="html")

```
### Mean Total Costs by HH
```{r,echo=F,results='asis'}

CostByHH <- rbind(Mean=sapply(lgroups,function(G){mean(lps$CostTot[G])}),
                       Median=sapply(lgroups,function(G){median(lps$CostTot[G])}))
CostByHHF <- formatC(CostByHH,digits=0,format="f",big.mark=",")
print(xtable(CostByHHF),type="html")

```


### Mean Outpatien Costs by Indv
```{r,echo=F,results='asis'}

OutpCostByIndv <- rbind(Mean=sapply(ligroups,function(G){mean(IndiHealth$OutpCost[G])}),
                       Median=sapply(ligroups,function(G){median(IndiHealth$OutpCost[G])}))
OutpCostByIndvF <- formatC(OutpCostByIndv,digits=0,format="f",big.mark=",")
print(xtable(OutpCostByIndvF),type="html")

```
### Mean Outpatien Costs by HH
```{r,echo=F,results='asis'}

OutpCostByHH <- rbind(Mean=sapply(lgroups,function(G){mean(lps$OutpCost[G])}),
                       Median=sapply(lgroups,function(G){median(lps$OutpCost[G])}))
OutpCostByHHF <- formatC(OutpCostByHH,digits=0,format="f",big.mark=",")
print(xtable(OutpCostByHHF),type="html")

```

### Mean Total Inp Costs by Indv

```{r,echo=F,results='asis'}

InpCostByIndv <- rbind(Mean=sapply(ligroups,function(G){mean(IndiHealth$InpCost[G])}),
                         Median=sapply(ligroups,function(G){median(IndiHealth$InpCost[G])}))
MeanInpCostByIndvF <- formatC(InpCostByIndv,digits=0,format="f",big.mark=",")
print(xtable(MeanInpCostByIndvF),type="html")

```

### Mean Total Inp Costs by HH
```{r,echo=F,results='asis'}

##HHInpCost

InpCostByHH <- rbind(Mean=sapply(lgroups,function(G){mean(lps$InpCost[G])}),
                         Median=sapply(lgroups,function(G){median(lps$InpCost[G])}))
InpCostByHHF <- formatC(InpCostByHH,digits=0,format="f",big.mark=",")
print(xtable(InpCostByHHF),type="html")


```




# Cost modeling:

```{r,echo=F,results='hide',message=F,warning=F}

OutpatientMeanCosts <-     sapply(OutPatGroups,function(G){
                                sapply(CCs,function(C){
                                         c <- OutPatCostTable$CareCenter==C
                                         mean(OutPatCostTable[c&G,"Overall_average"])
                                       })
                              })
OutpatientMeanCostsF <- formatC(OutpatientMeanCosts,digits=0,big.mark=",",format="f")
OutpatientMeanCostsF

OutpatientMedianCosts <-     sapply(OutPatGroups,function(G){
                                sapply(CCs,function(C){
                                         c <- OutPatCostTable$CareCenter==C
                                         median(OutPatCostTable[c&G,"Overall_average"])
                                       })
                              })
OutpatientMedianCostsF <- formatC(OutpatientMedianCosts,digits=0,big.mark=",",format="f")
OutpatientMedianCostsF


OutpatientModelCosts  <- (OutpatientMeanCosts +OutpatientMedianCosts)/2
OutpatientModelCosts["Traditional_Healer","PreID"] <-OutpatientModelCosts["Traditional_Healer","All"]
OutpatientModelCosts["National_Hospital","GeoID"] <- OutpatientModelCosts["National_Hospital","All"]
OutpatientModelCostsF <- formatC(OutpatientModelCosts,digits=0,big.mark=",",format="f")
OutpatientModelCostsF

```

### Mean Outpatient Costs by department

```{r,echo=F,results='asis'}

print(xtable(OutpatientMeanCostsF),type="html")

```

### Median Outpatient Costs by department
```{r,echo=F,results='asis'}

print(xtable(OutpatientMedianCostsF),type="html")

```

### Outpatient Cost Model by department
```{r,echo=F,results='asis'}

print(xtable(OutpatientModelCostsF),type="html")
ModelOutpCosts <-OutpatientModelCosts;
  
```


###Mean Inpatient Costs by department
```{r,echo=F,results='asis'}

## Print InpAllMeanCost
InpAllMeanCostF <- formatC(InpAllMeanCost,digits = 0,format = "f",big.mark = ",");
print(xtable(InpAllMeanCostF),type="html")

```
###Median Inpatient Costs by department
```{r,echo=F,results='asis'}

## Print InpAllMedianCost
print(xtable(formatC(InpAllMedianCost,digits = 0,format = "f",big.mark = ",")),type="html")

```

### Model Inpatient Costs
```{r,echo=F,results='asis'}

missing <- which(is.na(InpAllMeanCost))
ModelInpCosts <- (InpAllMeanCost + InpAllMedianCost)/2
##Get NA Model values filled in
for(I in missing){
  nrows <- length(InpAllMeanCost[,1])
  row <- I%%nrows;
  if(row==0){row <- nrows}
  col <- round(I/nrows);
  ## get valus from all
  ModelInpCosts[row,col] <- (InpAllMeanCost[row,"All"]  +
                               InpAllMedianCost[row,"All"])/2;
}
ModelInpCostsF=formatC(ModelInpCosts,digits=0,format="f",big.mark=",")
print(xtable(ModelInpCostsF),type="html")




```




###Inpatient Cost Patterns
```{r,echo=F,results='asis'}

a <- sapply(InPatGroups,function(G){InPatCostTable$Overall_average[G]})
boxplot(a,main="Overall Average for all Inpatient events by group")
boxplot(a,main="Overall Average for all Inpatient events by group (detail)",ylim=c(0,1e6))
means <- sapply(InPatGroups,function(G){mean(InPatCostTable$Overall_average[G])})



```

```{r,echo=F,results='asis'}

trim <- 12E6
trim <- 1E6
trim <- 1E5

PlotTrimedGroups  <- function (trim=12E6,trimLow=0,breaks=30) {
  keep <- InPatCostTable$Overall_average<trim & InPatCostTable$Overall_average>=trimLow;
  InPatCostTrim <- InPatCostTable[keep,];
  InPatTrimGroups <- lapply(InPatGroups,function(G){G[keep]})
  #Build the histograms
  h4 <- hist( InPatCostTrim$Overall_average[InPatTrimGroups[[4]]],breaks,plot=F)
  h1 <- hist( InPatCostTrim$Overall_average[InPatTrimGroups[[1]]],h4$breaks,plot=F)
  h2 <- hist( InPatCostTrim$Overall_average[InPatTrimGroups[[2]]],h4$breaks,plot=F)
  h3 <- hist( InPatCostTrim$Overall_average[InPatTrimGroups[[3]]],h4$breaks,plot=F)
  #create the composite bar plot
  area <- h1$breaks[2:length(h1$breaks)] - h1$breaks[1:(length(h1$breaks)-1)]
  area*h1$density
   T <- rbind.data.frame(area*h1$density,area*h2$density,area*h2$density)
   T <- rbind.data.frame(h1$counts,h2$counts,h2$counts)
  if (trimLow!=0){
    colnames(T)  <- as.character(h4$breaks)[2:length(colnames(T))]
  }else{
    colnames(T)  <- as.character(h4$breaks)[1:length(colnames(T))]
  }
  barplot(as.matrix(T),las=2,col=c(rgb(1,0,0),rgb(0,1,0),rgb(0,0,1)))
 }


```




```{r,echo=F,results='html'}

MeanInpCostByIndv <- sapply(ligroups,function(G){mean(IndivInpCost[G])})

```
### Median Inpatient Costs by department
```{r,echo=F,results='html'}

MedianInpCostByIndv <- sapply(ligroups,function(G){median(IndivInpCost[G])})

```


```{r,echo=F,results='html'}
 source("./SmallScripts/CostIndividualsCare.r")
```

IndivInpCost Has a numeric vector of each individual's estimated cost.

```{r,results='asis'}
boxplot(sapply(ligroups,function(G){IndivInpCost[G]}))
```





# Total Cost Distribution
```{r,echo=T,results='html'}

p <-ggplot(subset(lps,CostTot<2e7),aes(CostTot))
p <- p + geom_histogram()
p <- p + facet_grid(. ~ Group)
p

p <- qplot(Score,CostTot,data=lps)
p <- p + facet_grid(. ~ Group)
p <- p + stat_smooth(method="lm",se=F)
p

p <- qplot(Score,CostTot,data=subset(lps,CostTot<2E7))
p <- p + facet_grid(. ~ Group)
p <- p + stat_smooth(method="lm",se=F)
p

p <- qplot(Score,CostTot,data=subset(lps,CostTot<5E6))
p <- p + facet_grid(. ~ Group)
p <- p + stat_smooth(method="lm",se=F)
p

```

#Income VS Cost
```{r,results='html'}

p <- qplot(HH_Cash_income,CostTot,data=lps)
p

p <- qplot(HH_Cash_income,CostTot,data=subset(lps,HH_Cash_income<2e8))
p

p <- qplot(HH_Cash_income,CostTot,data=subset(lps,HH_Cash_income<5e7 & CostTot<2e7))
p

p <- qplot(HH_Cash_income,CostTot,data=subset(lps,HH_Cash_income<2e7 & CostTot<2e7))
p

p <- qplot(HH_Cash_income,CostTot,data=subset(lps,HH_Cash_income<5e6 & CostTot<2e7))
p <- aes(colour=Group)
p
```

# Total Inpatient Reported cost vs Income
```{r,results='html'}

p <- ggplot(lps,aes(x=HH_Cash_income,y=InpTotOveralRep))
p + geom_point(aes(colour=Group),size=2,alpha=.75)

p <- ggplot(subset(lps),
            aes(x=HH_Cash_income,y=InpTotOveralRep))
p + geom_point(aes(colour=Group),size=3,alpha=.75)

p <- ggplot(subset(lps,HH_Cash_income< 1e8 & InpTotOveralRep <2e7),
            aes(x=HH_Cash_income,y=InpTotOveralRep))
p + geom_point(aes(colour=Group),size=3,alpha=.75)


p <- ggplot(subset(lps,HH_Cash_income< 2.5e7 & InpTotOveralRep <5e6),
            aes(x=HH_Cash_income,y=InpTotOveralRep))
p + geom_point(aes(colour=Group),size=3,alpha=.75)

p <- ggplot(subset(lps,HH_Cash_income<3e7 & InpTotOveralRep <2e5 ),
            aes(x=HH_Cash_income,y=InpTotOveralRep))
p + geom_point(aes(colour=Group),size=3,alpha=.75)

p <- ggplot(subset(lps,HH_Cash_income<2e8 & InpTotOveralRep<10000 ),aes(x=HH_Cash_income,y=InpTotOveralRep))
p + geom_point(aes(colour=Group),size=2,alpha=.5)



p <- ggplot(subset(lps),
            aes(x=Score,y=InpTotOveralRep))
p + geom_point(aes(colour=Group),size=3,alpha=.75)

p <- ggplot(subset(lps,InpTotOveralRep < 1e6),
            aes(x=Score,y=InpTotOveralRep))
p + geom_point(aes(colour=Group),size=3,alpha=.75)

p <- ggplot(subset(lps,InpTotOveralRep < 1e6),
            aes(x=Score,y=InpTotOveralRep))
p + geom_point(size=3,alpha=.75) + facet_grid(.~Group)





```

# inpatient's who report no cost
```{r,results='asis'}
p <- ggplot(subset(lps,InpTotOveralRep==0),aes(x=HH_Cash_income))
p <- p + geom_histogram()
p <- p + facet_grid(. ~ Group)
p

```


```{r,results='asis'}
boxplot(sapply(lgroups,function(G){HHInpCost[G]}),ylim=c(0,7000000))
```

```{r,results='html'}

p <-ggplot(lps,aes(x=Score))
p <- p + geom_histogram(aes(y=..density..,color=Group)) + geom_density(fill=NA,aes(color=Group),size=2)
p <- p + facet_grid(. ~ Group)
p

```




##Relationship between sum of Overall_Average for each Service vs Total Overall Average
```{r,echo=T,results='html'}

qplot(OutTotOveralRep,OutTotRep,data=subset(lps,OutTotOveralRep<2500000))

```
## Num Illnesses
```{r,echo=T,results='html'}

ggplot(IndiHealth,aes(x=NumIllnesses))+geom_histogram(binwidth=1)+facet_grid(.~Group)

qplot(NumIllnessesTotal,InpTotOveralRep,data=lps)

qplot(Age,NumIllnesses,data=IndiHealth)
library("GGally")
ggpairs(IndiHealth[,c("Age","Gender","NumIllnesses","CostTot","Group")])
           


```
