---
title: "Sampling Analysis"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
    html_document:
        toc: true
        toc_depth: 5
        number_sections: true
---

```{r, echo=F, message=F}

load(file="OOPCrossAnalysis.RData")
library("ggplot2")
library("xtable")
library("reshape")
library("scales")

opts_chunk$set(comment=NA, fig.height=4, fig.width=7, fig.align='center')
knitr::opts_chunk$set(cache=TRUE)
knitr::opts_chunk$set(dev='png')

outdir <- "./html/MNCHQuestions_files/"


printTT <- function(tb,caption) {
  ## write.csv(tb,file=paste(outdir,caption,".csv",sep=""))
  tbm <- addmargins(tb)
  ftb <-ftable(tbm)
  ct <- ncol(tbm);
  ftb <- format(ftb)
  cn <- ncol(ftb)-ct
  print(xtable(ftb,
               caption=paste("Number",caption),
               align=c(rep("l",cn+1),
                       rep("c",ct))
               ),
        type='html',
        html.table.attributes = "border = '1', align = 'center'")
  ptb <- addmargins(prop.table(tb)*100)
  ftb <-ftable(ptb)
  ct <- ncol(ptb);
  ftb <- format(ftb,digits=2)
  cn <- ncol(ftb)-ct
  print(xtable(ftb,
               caption=paste("Percent",caption,"by cell"),
               align=c(rep("l",cn+1),
                       rep("c",ct))
               ),
        type='html',
        html.table.attributes = "border = '1', align = 'center'")
  ptb <-  addmargins(prop.table(tb,1)*100)
  ftb <-ftable(ptb)
  ct <- ncol(ptb);
  ftb <- format(ftb,digits=2)
  cn <- ncol(ftb)-ct
  print(xtable(ftb,
               caption=paste("Percent",caption,"by row"),
               align=c(rep("l",cn+1),
                       rep("c",ct))
               ),
        type='html',
        html.table.attributes = "border = '1', align = 'center'")  
  ptb <-  addmargins(prop.table(tb,2)*100)
  ftb <-ftable(ptb)
  ct <- ncol(ptb);
  ftb <- format(ftb,digits=2)
  cn <- ncol(ftb)-ct
  print(xtable(ftb,
               caption=paste("Percent",caption,"by col"),
               align=c(rep("l",cn+1),
                       rep("c",ct))
               ),
        type='html',
        html.table.attributes = "border = '1', align = 'center'")  

}



printT <- function(tb,caption) {
  ## write.csv(tb,file=paste(outdir,caption,".csv",sep=""))
  ftb <-ftable(tb)
  ct <- ncol(tb);
  ftb <- format(ftb)
  cn <- ncol(ftb)-ct
  print(xtable(ftb,
               catption=paste("Percent",caption),
               align=c(rep("l",cn+1),
                       rep("c",ct))
               ),
        type='html')
}


```        



# Breakdown of CU2 and CU5

## Expect 210 CU2 and 366 CU5

## Find 366 CU2 and 596 CU5

All respondents for Q4 and Q5 are the same 366 mothers considered to
be the CU2 mothers involved in MNCH evaluation.

CU5 Mothers are respondents to question 7 about child addmittance
events. 596 mothers respond with 82 of them reporting a child
admittance event.
## CU2 Breakdown

```{r, echo=F}

cat("Percent of CU2 mothers in each group (q4_1 respondents)")
CU2All <- with(lps,table(ifelse(!is.na(Mother_ID),
                                "CU2",
                                "No-CU2")))

print(addmargins(with(lps,table(Group,
                                ifelse(!is.na(Mother_ID),
                                       "CU2",
                                       "No-CU2")
                                ))),
      digits=2   
      )


cat("Percent of CU2 mothers in each group (q4_1 respondents)")
CU2All <- with(lps,table(ifelse(!is.na(Mother_ID),
                                "CU2",
                                "No-CU2")))

print(addmargins(prop.table(with(lps,rbind(table(Group,
                                           ifelse(!is.na(Mother_ID),
                                                  "CU2",
                                                  "No-CU2")
                                           ),All=CU2All)),1)*100)[1:4,],
      digits=2   
      )

```

## CU5 Detailed breakdown 

```{r, echo=F}

cat("Number of CU5 mothers by group (q7_5 respondents)")
print(addmargins(with(lps,table(Group,
                   ifelse(!is.na(Child_Admitted_Past_year),
                          "CU5",
                          "No-CU5")
                   ))))

cat("Percent of CU5 mothers in dataset (q7_5 respondents)")
print(addmargins(prop.table(with(lps,table(Group,
                                           ifelse(!is.na(Child_Admitted_Past_year),
                                                  "CU5",
                                                  "No-CU5")
                                           )))*100),
      digits=2   
      )

cat("Percent of CU5 mothers in each group (q7_5 respondents)")
CU5All <- with(lps,table(ifelse(!is.na(Child_Admitted_Past_year),
                                "CU5",
                                "No-CU5")))
print(addmargins(prop.table(with(lps,rbind(table(Group,
                                           ifelse(!is.na(Child_Admitted_Past_year),
                                                  "CU5",
                                                  "No-CU5")
                                           ),All=CU5All)),1)*100)[1:4,],
      digits=2   
      )

cat("Percent of CU5 mothers by group (q7_5 respondents)")
print(addmargins(prop.table(with(lps,table(Group,
                                           ifelse(!is.na(Child_Admitted_Past_year),
                                                  "CU5",
                                                  "No-CU5")
                                           )),2)*100),
      digits=2   
      )



cat("Number of CU5 child admittance (q7_5 affirmative)")
print(addmargins(with(lps,table(Group,
                   ifelse(Child_Admitted_Past_year==1,
                          "Child Admitted",
                          "No Child Admitted")
                   )))
      )

cat("Percent of CU5 child admittance (q7_5 affirmative)")
print(addmargins(prop.table(with(lps,table(Group,
                   ifelse(Child_Admitted_Past_year==1,
                          "Child Admitted",
                          "No Child Admitted")
                   )))*100),
      digits=2
      )



```
## Breakdown of CU5 and CU2 responders
```{r, echo=F}

cat(        "Breakdown of CU5 and CU2 responders")
print(ftable(addmargins(with(lps,
                       table(Group,
                             ifelse(!is.na(Child_Admitted_Past_year),
                                    "CU5",
                                    "No-CU5"),
                             ifelse(!is.na(Mother_ID),
                                    "CU2",
                                    "No-CU2")
                             )))
      ))

cat(        "Percent of CU5 and CU2 responders")
print(ftable(addmargins(prop.table(with(lps,
                       table(Group,
                             ifelse(!is.na(Child_Admitted_Past_year),
                                    "CU5",
                                    "No-CU5"),
                             ifelse(!is.na(Mother_ID),
                                    "CU2",
                                    "No-CU2")
                             )))*100)),
      digits=2)

```      

# Confidence intervals

## CU2 Confidence intervals


```{r, echo=F}
cat("Num CU2 Mothers")
print(NumMothers)

cat("Confidence intervals are +/- the following percents for probabilities in yes/no questions in CU2:")
print(100*(sapply(NumMothers,function(N){prop.test(N/2,N,correct=F)$conf.int})[2,]-.5),digits=2)

```

## CU5 Confidence intervals

```{r, echo=F}

NCU5 <- with(lps,sapply(levels(Group),function(G){sum(!is.na(Child_Admitted_Past_year[Group==G]))}))
NCU5  <- c(NCU5 ,All=sum(NCU5 ))
cat("Num CU5 Mothers")
print(NCU5)

cat("Confidence intervals are +/- the following percents for probabilities in yes/no questions in CU5:")
print(100*(sapply(NCU5,function(N){prop.test(N/2,N,correct=F)$conf.int})[2,]-.5),digits=2)

```
# Village Distributions
## PreID Vs GeoID HH
```{r, echo=F}

NPreID_HH <- with(Villages,sapply(c(1,2),function(P){sum(X..HH.Total[P==Pre.ID])}))
names(NPreID_HH) <- c("PreID","GeoID")
cat("Total number of HHs in areas:")
print(c(NPreID_HH,All=sum(NPreID_HH)))

cat("Percent of HHs in areas:")
print(100*(NPreID_HH/sum(NPreID_HH)),digits=2)

cat("Percent of GeoID HHs in survey")
print(100*(269/930),digits=3)

cat("Percent of GeoID HHs sampled")
print(100*(NumGroups[2]/NPreID_HH[2]),digits=3)

cat("Percent of non GeoID HHs sampled")
print(100*((NumGroups[4]-NumGroups[2])/NPreID_HH[1]),digits=3)

Villages$PreID <- factor(Villages$Pre.ID,labels=c("PreID","GeoID"))

## p <- ggplot(data=Villages)
## p <- p + geom_bar(aes(x=PreID,y=sum(X..HH.Total)),binwidth=1)
## print(p)
Villages$NHEF <- as.numeric(gsub(",","",as.character(Villages[,23])))


with(subset(Villages,PreID=="PreID"),NHEF/X..HH.Total)
with(subset(Villages,PreID=="GeoID"),NHEF/X..HH.Total)




```
# Population Distribution
```{r}

Villages$VillageNum <- factor(Villages$VillageNum)
## p <- qplot(Year, Frequency, data = Data, geom = "bar", fill = Category,     theme_set(theme_bw()))
p <- qplot(VillageNum,X..HH.Total,data=Villages,geom = "bar", stat="identity",fill= PreID)
p <- p + theme(axis.text.x = element_text(angle = 90, hjust = 1))
print(p)


```
