---
title: "Cost Modeling"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
    html_document:
        toc: true
        toc_depth: 5
        number_sections: true
---


# General Inpatient and Outpatient Costs
```{r,echo=F,results='hide',message=F,warning=F}

opts_chunk$set(comment=NA, fig.height=4, fig.width=7, fig.align='center')
knitr::opts_chunk$set(cache=TRUE)
knitr::opts_chunk$set(dev='png')

library("ggplot2")
library("xtable")
source("LoadData.R")
source("./SmallScripts/Utility.r")
library("reshape")
library("scales")
library("plyr")
library(Hmisc)
set.seed(0)

MDM <- T

```

```{r, echo=F, results='asis'}

source("SmallScripts/ComputeCosts.r")

```

# Inpatient and outpatient costs by facility

## Outpatient CU5

### Num Outpatient CU5 Reports by Facility
```{r, echo=F}

with(subset(OutPat,Total<500000 & Age < 5),tapply(Total,list(Facility=Facility,Group=Group),FUN=length))

```


### Mean Outpatient CU5
```{r, echo=F}

OutPCU5Mean <- with(subset(OutPat,Total<500000 & Age < 5),tapply(Total,list(Facility=Facility,Group=Group),FUN=mean))
OutPCU5Mean

```
### Median Outpatient CU5
```{r, echo=F}

OutPCU5Median <- with(subset(OutPat,Total<500000 & Age < 5),tapply(Total,list(Facility=Facility,Group=Group),FUN=median))
OutPCU5Median

```
### Model Outpatient CU5
```{r, echo=F}

OutPCU5 <- (OutPCU5Mean+OutPCU5Median)/2
OutPCU5 <- sapply(levels(OutPat$Group),function(G){OutPCU5[is.na(OutPCU5[,G]),G] <- OverallCosts["OutP_CU5",G]; return(OutPCU5[,G])})
OutPCU5 <- t((t(OutPCU5) + OverallCosts["OutP_CU5",])/2)
OutPCU5

```

## Outpatient

### Num Reports by facility
```{r, echo=F}

with(subset(OutPat,Total<500000 & Age >= 5),tapply(Total,list(Facility=Facility,Group=Group),FUN=length))

```

### Mean Outpatient
```{r, echo=F}

OutPCMean <- with(subset(OutPat,Total<500000 & Age >= 5),tapply(Total,list(Facility=Facility,Group=Group),FUN=mean))
OutPCMean

```
### Median Outpatient
```{r, echo=F}

OutPCMedian <- with(subset(OutPat,Total<500000 & Age >= 5),tapply(Total,list(Facility=Facility,Group=Group),FUN=median))
OutPCMedian

```

### Model Outpatient
```{r, echo=F}


OutPC <- (OutPCMean+OutPCMedian)/2
OutPC <- sapply(levels(OutPat$Group),function(G){OutPC[is.na(OutPC[,G]),G] <- OverallCosts["OutP",G]; return(OutPC[,G])})
OutPC <- t((t(OutPC) + OverallCosts["OutP",])/2)
OutPC


```
## Inpatient CU5

### Num Inptatient CU5 Reports by Facility
```{r, echo=F}

InPF <- sub("Overnight_At_","",grep("Overnight_At_",names(IH),value=T))
with(subset(InPat,Facility %in% InPF & Total<1000000 & Age < 5),tapply(Total,list(Facility=factor(Facility),Group=Group),FUN=length))


```

### Mean Inpatient CU5
```{r, echo=F}


InPCU5Mean <- with(subset(InPat,Facility %in% InPF & Total<1000000 & Age < 5),tapply(Total,list(Facility=factor(Facility),Group=Group),FUN=mean))
InPCU5Mean

```
### Median Inpatient CU5
```{r, echo=F}

InPCU5Median <- with(subset(InPat,Facility %in% InPF & Total<1000000 & Age < 5),tapply(Total,list(Facility=factor(Facility),Group=Group),FUN=median))
InPCU5Median

```
### Model Inpatient CU5
```{r, echo=F}


InPCU5 <- (InPCU5Mean+InPCU5Median)/2
InPCU5 <- sapply(levels(InPat$Group),function(G){InPCU5[is.na(InPCU5[,G]),G] <- OverallCosts["InP_CU5",G]; return(InPCU5[,G])})
InPCU5 <- t((t(InPCU5) + OverallCosts["InP_CU5",])/2)

InPCU5 <- rbind(InPCU5,
      NH=OverallCosts["InP_CU5",],
      PC=OverallCosts["InP_CU5",])
InPCU5

```

## Inpatient
### Num Inpatient Reports by Facility
```{r, echo=F}

with(subset(InPat,Facility %in% InPF & Total<1000000 & Age >= 5),tapply(Total,list(Facility=factor(Facility),Group=Group),FUN=length))

```

### Mean Inpatient
```{r, echo=F}

InPCMean <- with(subset(InPat,Facility %in% InPF & Total<1000000 & Age >= 5),tapply(Total,list(Facility=factor(Facility),Group=Group),FUN=mean))
InPCMean

```
### Median Inpatient
```{r, echo=F}

InPCMedian <- with(subset(InPat,Facility %in% InPF & Total<1000000 & Age >= 5),tapply(Total,list(Facility=factor(Facility),Group=Group),FUN=median))
InPCMedian

```

### Model Inpatient
```{r, echo=F}


InPC <- (InPCMean+InPCMedian)/2
InPC <- sapply(levels(InPat$Group),function(G){InPC[is.na(InPC[,G]),G] <- OverallCosts["InP",G]; return(InPC[,G])})
InPC <- t((t(InPC) + OverallCosts["InP",])/2)
InPC


```


# Individual Costs

## OutPatient Costs by Individual
```{r, echo=F}

##Stricly Outpatient costed care options

OutF <- c("HV","PP","TH","RH")
IH$CostOutP <- 0
for (G in levels(InPat$Group)){
  for (Fl in OutF) {
    IH$CostOutP[IH$Group==G & IH$Age<5 & IH[,paste("Care_At",Fl,sep="_")]] <-
      IH$CostOutP[IH$Group==G & IH$Age<5 & IH[,paste("Care_At",Fl,sep="_")]] +
      OutPCU5[Fl,G]
  }
}
for (G in levels(InPat$Group)){
  for (Fl in OutF) {
    IH$CostOutP[IH$Group==G & IH$Age>=5 & IH[,paste("Care_At",Fl,sep="_")]] <-
      IH$CostOutP[IH$Group==G & IH$Age>=5 & IH[,paste("Care_At",Fl,sep="_")]] +
      OutPC[Fl,G]
  }
}
for (G in levels(InPat$Group)){
  for (Fl in InPF) {
    IH$CostOutP[IH$Group==G & IH$Age<5 & IH[,paste("Overnight_At",Fl,sep="_")]=="Day" ] <-
      IH$CostOutP[IH$Group==G & IH$Age<5 & IH[,paste("Overnight_At",Fl,sep="_")]=="Day"] +
      OutPCU5[Fl,G]
  }
}
for (G in levels(InPat$Group)){
  for (Fl in InPF) {
    IH$CostOutP[IH$Group==G & IH$Age>=5 & IH[,paste("Overnight_At",Fl,sep="_")]=="Day" ] <-
      IH$CostOutP[IH$Group==G & IH$Age>=5 & IH[,paste("Overnight_At",Fl,sep="_")]=="Day"] +
      OutPC[Fl,G]
  }
}


OutPMeanByIndiv <- with(subset(IH),aggregate(CostOutP,by=list(Group=Group),FUN=mean))
names(OutPMeanByIndiv)[2] <- "mean"
OutPMeanByIndiv


OutPMeanByIndiv <- with(subset(IH,CostOutP!=0),aggregate(CostOutP,by=list(Group=Group),FUN=mean))
names(OutPMeanByIndiv)[2] <- "mean"
OutPMeanByIndiv

```



## InPatient Costs by Individual
```{r, echo=F}

IH$CostInP <- 0
for (G in levels(InPat$Group)){
  for (Fl in InPF) {
    IH$CostInP[IH$Group==G & IH$Age<5 & IH[,paste("Overnight_At",Fl,sep="_")]=="Overnight" ] <-
      IH$CostInP[IH$Group==G & IH$Age<5 & IH[,paste("Overnight_At",Fl,sep="_")]=="Overnight"] +
      InPCU5[Fl,G]
  }
}
for (G in levels(InPat$Group)){
  for (Fl in InPF) {
    IH$CostInP[IH$Group==G & IH$Age>=5 & IH[,paste("Overnight_At",Fl,sep="_")]=="Overnight" ] <-
      IH$CostInP[IH$Group==G & IH$Age>=5 & IH[,paste("Overnight_At",Fl,sep="_")]=="Overnight"] +
      InPC[Fl,G]
  }
}
if(sum(rowSums(IH[,grep("Overnight_At",names(IH),value=T)]=="Overnight")>0)!=sum(IH$CostInP>0)){
  stop("Problem!!!, Overnights don't add up to total overnights")
}

InPMeanByIndiv <- with(IH,aggregate(CostInP,by=list(Group=Group),FUN=mean))
names(InPMeanByIndiv)[2] <- "mean"
InPMeanByIndiv

InPMeanByIndiv <- with(subset(IH,CostInP!=0),aggregate(CostInP,by=list(Group=Group),FUN=mean))
names(InPMeanByIndiv)[2] <- "mean"
InPMeanByIndiv


```
## Total Costs by Individual

```{r , echo=F}

PCMeanByIndiv <- with(subset(IH),aggregate(CostInP + CostOutP,by=list(Group=Group),FUN=mean))
names(PCMeanByIndiv)[2] <- "mean"
PCMeanByIndiv


PCMeanByIndiv <- with(subset(IH,CostInP!=0 | CostOutP!=0),aggregate(CostInP + CostOutP,by=list(Group=Group),FUN=mean))
names(PCMeanByIndiv)[2] <- "mean"
PCMeanByIndiv


```

## Total Costs by HH
```{r , echo=F}

PCMeanByHH <- with(with(IH,aggregate(CostInP + CostOutP,by=list(Serial=Serial,Group=Group),FUN=sum)),
                   aggregate(x,by=list(Group=Group),FUN=mean))
names(PCMeanByHH)[2] <- "mean"
PCMeanByHH

```


```{r , echo=F}

AllCostMeansByGroup <- rbind(OutPMeanByIndiv[,2],InPMeanByIndiv[,2],PCMeanByIndiv[,2],PCMeanByHH[,2])
rownames(AllCostMeansByGroup) <- c("Outpatient by Indv",
                                   "Inpatient by Indv",
                                   "Total by Indv",
                                   "Total by HH")
colnames(AllCostMeansByGroup) <- levels(IH$Group)
AllCostMeansByGroup

```
## Provincial Cost Estimates

### Sample to Province Ratios

```{r , echo=F}



```
