---
title: "PreId_Comparison"
author: "Leah Hale"
date: "29/04/2015"
output: html_document
---


```{r,results='hide'}

library("xtable")
source("LoadData.R");

source("AnalyzeGroups.R");

# demsTable<-data.frame();
# 
# HEFCard_by_PreId <- c(sum(lps[HEFCard,]$PreId),sum(!lps[HEFCard,]$PreId));
# GVTPoor_by_PreId <- c(sum(lps[GVTPoor,]$PreId),sum(!lps[GVTPoor,]$PreId));
# NoInsu_by_PreId  <- c(sum(lps[NoInsu,]$PreId), sum(!lps[NoInsu,]$PreId));
#             
# 
# 
# demsTable <- rbind(HEFCard_by_PreId,GVTPoor_by_PreId,NoInsu_by_PreId);
# 
# demsTable<-cbind(demsTable,rowSums(demsTable));
# rownames(demsTable)<-c("HEF Card Holder","Govenment Poor List","No Insurance")
# colnames(demsTable)<-c("PreId","Geo","Row Total");
# print(xtable(demsTable),"html")

```
```{r, results='hide'}
```
# Demographics (HH)
```{r,results='asis'}
print(xtable(demsTable),"html")
```
### P Values for demographics
```{r,results='asis'}
print(xtable(demsSigTable),"html")
```

# HC Seeking
```{r, results='asis'}
print(xtable(hcSeek),"html")
```

```r sum(HEF_PreID & NoAssist)``` persons are on both the HEF_PreId and the NoAssist List we will cound them as HEF.

### p values for health seeking
```{r, results='asis'}
print(xtable(hcSeekSig,digits=4),"html")
```

```r sum (HEF_PreID & Geo_Poor)```

which(HEF_PreID & NoAssist)


```{r,results='hide'}
HEF_PreID <-lps$PreId & HEFCard;
Geo_Poor  <-!lps$PreId & GVTPoor;
NoAssist  <-lps$PreId & NoInsu;

lgroups <- list(HEF_PreID,Geo_Poor,NoAssist)
```

#Family size
```{r} 
wilcox.test(HH_NumPeople~HEF_PreID,data=lps[OnAList])
``` 
HEF to all in sample group.
```{r}
wilcox.test(HH_NumPeople~Geo_Poor,data=lps[OnAList])
``` 
GeoPoor to all in sample group.
```{r}
wilcox.test(HH_NumPeople~NoAssist,data=lps[OnAList])
``` 
No Assist to all in sample group.


#Num Peopls
```{r}
n1<-which(names(lps)=="q2_1_2_30")
vname<-!is.na(lps[,n1:(n1+29)])
nnames<-rowSums(vname)
sum (!lps$HH_NumPeople == nnames)

hist(lps$HH_NumPeople - nnames)
hist(lps$HH_NumPeople)
hist(nnames)
```
Num names matches num people every times


#Check Service Usage 

```{r,results='hide'}
si<-which(names(IndiHealth)=="Care At- No care");
ei<-which(names(IndiHealth)=="Care At - Do not know")
NCareSpec <- sum(IndiHealth$Illness[rowSums(!is.na(IndiHealth[si:ei]))==0]==1);

```

There are ```r NCareSpec``` individuals who where reported as being ill but nocare (not even 'no care') was specified.