---
title: "Thesis Analysis"
date: "02/06/2015"
output:
    html_document:
        toc: true
        toc_depth: 4
        number_sections: true
---

# Background
```{r,echo=F,results='hide',message=F,warning=F}

opts_chunk$set(comment=NA, fig.height=4, fig.width=7, fig.align='center')
knitr::opts_chunk$set(cache=TRUE)
knitr::opts_chunk$set(dev='png')

library("ggplot2")
library("xtable")
source("LoadData.R")
source("./SmallScripts/Utility.r")
library("reshape")
library("scales")
set.seed(0)

```

# Question: does HEF improve equity of MNCH care across poverty levels?

## Identify the correlation between wealth and MNCH care score

## Determine weather GeoID and/or PreID show improved MNCH score while controlling for wealth.

```{r }

stat_sum_single <- function(fun, geom="point", ...) {
  stat_summary(fun.y=fun, colour="orange", geom=geom, size = 4, ...)
}
Mothers$Class <- cut(Mothers$Score,8)
p <- ggplot(data=Mothers,aes(x=Class,y=Score_MNCH))
p <- p + geom_point(aes(color=Group),  position=position_jitter(w=.4,h=0),alpha=.2)
p <- p + stat_sum_single(mean)
p <- p + stat_summary(fun.data = "mean_cl_boot", colour = "red")
p <- p + stat_smooth(method = "lm",aes(colour=Group),se=F)
p <- p + stat_smooth(method = "lm",colour="Black",se=F)

p <- p + facet_grid(.~Group)
p <- p + theme(axis.text.x = element_text(angle = 90, hjust = 1))
p



```



# who are the poor in Laos ?

## Does the existing PCA effectively measure poverty?

### What metric do we have to evaluate the PCA



# do the poor have different MNCH results than the non-poor?

because this is about equity...  Overall, Laos has had big strides in improving
MNCH on a national level.  But, if this is not happening in an
equitable fashion, we need to know and look at areas of improvement

## what are the driving factors in MNCH results?

# Are MNCH scores differences supply or demand side?

